Z-Resonance at LEP

### 2010-10-11 Z0-Publikation/tex/paper-template.tex
fixes Robert

The particle detector LEP is built in a way as can be seen in \fref{aufbau}.
\begin{figure}[htb]
 \centering
 \includegraphics[page=5,viewport=286 620 508 765,clip,%
  width=\columnwidth,keepaspectratio]{../../Z0/docs/Z0ResFprakt}
 \caption{Design of the L3 detector.}% \cite{pic}.}
%  \todo[inline]{soll hier eine quelle hin?}
 \label{fig:aufbau}
\end{figure}
There are layers of components with different purposes. Starting from the
interaction point, these are the tracking chamber, the electromagnetic
calorimeter, the hadronic calorimeter and finally the muon chamber.

@@

\subsection{Hadronic events}
As it is now known how to extract hadronic events out of the data, it is
possible to determine the hadronic cross section using the following formula:
\begin{equation}
σ_{\mathrm{had}} = \frac{N}{Lε},
\end{equation}
where ε is the efficiency of the cuts. This efficiency could be calculated
using the following equation:
\begin{equation}
ε = \frac{N’_{\mathrm{MC}}}{N_{\mathrm{MC}}},
\end{equation}
where $N’_{\mathrm{MC}}$ is the number of Monte Carlo events that passed the
hadron cuts and $N_{\mathrm{MC}}$ is the total number of events in the Monte
Carlo file.

@@

% These cross sections have then been used as data for a fit (see \fref{fit_hadrons}).
These cross sections have been used then to fit the Breit-Wigner distribution as
seen in \fref{fit_hadrons}.
By fitting the data
points the overall hadronic cross section $σ_0^{\mathrm{had}}$, the mass $M_Z$
and the decay width $Γ_Z$ of the $Z^0$-boson could be determined. The results
can be found in \tref{results}.

@@

% \begin{thebibliography}{}
% \baselineskip=0.38cm
% \bibitem{pic} http://ams.pg.infn.it/ams-italy/pub/5\_5.htm
% 
% \end{thebibliography}
% 
% \listoftodos

>>>>

The particle detector LEP is built in a way as can be seen in \fref{aufbau}.
\begin{figure}[htb]
 \centering
 \includegraphics[page=5,viewport=286 620 508 765,clip,%
  width=\columnwidth,keepaspectratio]{../../Z0/docs/Z0ResFprakt}
 \caption{Design of the L3 detector \cite{pic}.}
%  \todo[inline]{soll hier eine quelle hin?}
 \label{fig:aufbau}
\end{figure}
There are layers of components with different purposes. Starting from the
interaction point, these are the tracking chamber, the electromagnetic
calorimeter, the hadronic calorimeter and finally the muon chamber.

@@

\subsection{Hadronic events}
As it is now known how to extract hadronic events out of the data, it is
possible to determine the hadronic cross section using the following formula:
\begin{equation}
σ_{\mathrm{had}} = \frac{N}{Lε},
\end{equation}
where ε is the efficiency of the cuts. The acceptance can be interpreted as an
additional factor set to 1, which is included in the efficiency. This efficiency
could be calculated using the following equation:
\begin{equation}
ε = \frac{N’_{\mathrm{MC}}}{N_{\mathrm{MC}}},
\end{equation}
where $N’_{\mathrm{MC}}$ is the number of Monte Carlo events that passed the
hadron cuts and $N_{\mathrm{MC}}$ is the total number of events in the Monte
Carlo file.

@@

% These cross sections have then been used as data for a fit (see \fref{fit_hadrons}).
These cross sections have been used then to fit the Breit-Wigner distribution as
seen in \fref{fit_hadrons}. Additionally there is a second graph shown, which
is derived by the Breit-Wigner fit, but takes account for QCD effects like
initial and final state radiation.
By fitting the data
points the overall hadronic cross section $σ_0^{\mathrm{had}}$, the mass $M_Z$
and the decay width $Γ_Z$ of the $Z^0$-boson could be determined. The results
can be found in \tref{results}.

@@

\begin{thebibliography}{}
\baselineskip=0.38cm
\bibitem{pic} http://ams.pg.infn.it/ams-italy/pub/5\_5.htm
\bibitem{tdr} CERN (1984). "LEP design report". Geneva.
\bibitem{pdb} C. Amsler et al. (2008). "Review of Particle Physics". Physics Letters B 667

\end{thebibliography}
% 
% \listoftodos
